% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=mygreylink     % can put red here to visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.30}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{\LARGE Ian Yang} & \href{mailto:me@iany.me}{me@iany.me} \\
    {\small 8 years experience, Software Engineer, Shanghai} & {\small Phone: \texttt{15658018270}} \\
    {\footnotesize Bachelor, 30 years old} & \\
	\end{tabular*}
\\
\vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Profile}

\begin{itemize}
\item 4 years experience on web application development as a full stack
  engineer. Expertized in Ruby on Rails and JavaScript.
\item Accomplished software engineer specializing in C/C++ high
  performance service development in Linux.
\item Experianced in the domain advertising, information retrieval, machine learning and data
  mining.
\item Solid foundation in computer sciense and math.
\item Proven record track to designing and implementing flexible solutions for
  large scale system.
\item Software engineer best pracitices enthusiast.
\end{itemize}

\resheading{Experience}

\begin{itemize}
\item
  \ressubheading{\href{http://www.intridea.com}{Intridea}}{Work at Home}{%
    Software Engineer}{Feb. 2011 -- Present}

  { \footnotesize
    \begin{itemize}
      \resitem{Mainly worked in Ruby/Ruby on Rails client projects.}

      \resitem{Delivered a full featured web POS system based on HTML5 to the
        happy and satisfied client.}

      \resitem{Participated in refactoring and performance tuning of legacy
        Rails apps. In one project, decreased the job processing time from 2 hours to half an hour, and the heroku cost is
        reduced from \$500 per month to \$80.}
    \end{itemize}
  }

\item
  \ressubheading{\href{http://www.izenesoft.com/EN/home.html}{iZENEsoft}}{Shanghai}{%
    Software Engineer}{Jan. 2008 -- Feb. 2011}

  { \footnotesize
    \begin{itemize}
      \resitem{Proposed the new service-oriented architecture. Reduced the
        dependencies between componenets. Redesigned and implemented the API
        module of the search engine. The new API uses MVC to decouple
        components. It is much more easier to maintain and extend.}

      \resitem{Researched, evaluated and implemented various information
        retrieval and machine learning algorithms.}

      \resitem{Profiled and optimized the enterprise search engine. Refactored
        many bad smell legacy code and pushed other to write good style code.}

    \end{itemize}
  }

\item \ressubheading{\href{http://www.augmentum.com/}{Augmentum}}{Shanghai}{%
      Software Engineer}{Jul. 2006 -- Dec. 2007}

  { \footnotesize
    \begin{itemize}
      \resitem{Led a team to maintain and add new features to an ad server with
        thousands of publisher sites and billions of ads served
        daily.}
      
      \resitem{Rewrote the ad logging module and implemented a MySQL replication
        system to lighten the burden on database, which is the bottle neck of
        the whole system}
      
      \resitem{Designed and implemented some key algorithm, such as IP location
        lookup, timezone conversion}

    \end{itemize}
  }
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
\begin{itemize}
\item \ressubheading{Central Source University}{Hunan Province}{%
    Bachelor of Computer Science \& Technique}{Sep. 2002 -- Jun. 2006}

  { \footnotesize
    \begin{itemize}
      \resitem{At school I won scholarships twice}
    \end{itemize}
  }

\end{itemize} % End Education list  

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Skills}
	\begin{description}
		\item[Languages:] { \footnotesize C/C++, Ruby, Java Script, HTML, CSS, \LaTeX }
		\item[Platform:] { \footnotesize Proficient in Linux especially administration. }
    \item[Framework:] { \footnotesize Boost ASIO, RoR, Backbone, Restful Web Service}
		\item[Software:] { \footnotesize Keen on the best open source tools,
          libraries to accomplish the tasks. E.g. Emacs, Bootstrap, Boost, Jenkins }
	\end{description} % End Skills list

\end{document}
